R markdown project
=====================================
Instruction
It is now possible to collect a large amount of data about personal movement using activity monitoring devices such as a Fitbit, Nike Fuelband, or Jawbone Up. These type of devices are part of the ???quantified self??? movement ??? a group of enthusiasts who take measurements about themselves regularly to improve their health, to find patterns in their behavior, or because they are tech geeks. But these data remain under-utilized both because the raw data are hard to obtain and there is a lack of statistical methods and software for processing and interpreting the data.

##Loading and preprocessing the data
```{r}
if(!file.exists("Activity monitoring data.zip")){
  temp<- tempfile() 
  download.file("https://d396qusza40orc.cloudfront.net/repdata/data/activity.zip",temp)
  unzip(temp)
  unlink(temp)
}
activity <- read.csv("activity.csv")
activity$interval <- factor(data$interval)
naindex <- is.na(as.character(activity$steps))
actnona<- activity[!naindex,]
head(actnona)
stepsfordays <- aggregate(steps~date, data=actnona, sum)
head(stepsfordays)
```

##What is mean total number of steps taken per day?
```{r}
hist(stepsfordays$steps, breaks=20, col="red", xlab="Steps", main="Total number of steps")
mean(stepsfordays$steps)
median(stepsfordays$steps)
```

##What is the average daily activity pattern?
```{r}
stepsperinterval <- aggregate(actnona$steps, by=list(interval=actnona$interval), FUN= mean)
colnames(stepsperinterval) <- c("interval", "avgsteps")
plot(stepsperinterval$interval, stepsperinterval$avgsteps, type="l", 
     xlab="Interval", ylab="steps", main="average daily pattern", col="orange")
maxsteps <- max(stepsperinterval$avgsteps)
maxinterval <- stepsperinterval[which.max(stepsperinterval$avgsteps),]$interval
maxinterval
```

##Imputing missing values
```{r}
naindex1 <- which(is.na(as.character(activity$steps)))
finaldata <- activity
finaldata[naindex1,]$steps <- unlist(lapply(naindex1, FUN=function(naindex1){
  stepsperinterval[activity[naindex1,]$interval==stepsperinterval$interval,]$avgsteps
}))
finalsteps <- aggregate(steps~date, data=finandata, sum)
hist(as.numeric(finalsteps$steps), breaks = 20, col="red", xlab="Number of Steps", main="Histogram of the total number
     of steps taken each day")
mean(finalsteps$steps)
median(finalsteps$steps)
```

##Are there any differences in activity patterns between weekdays and weekends
```{r}
finaldata$day <- as.factor(weekdays(finaldata$date))
finaldata$isweekday <- ifelse(!(finaldata$day %in% c("Saturday", "Sunday")), TRUE, FLASE)
weekdaysdata <- finaldata[finaldata$isweekday,]
stepsperinverval-weekdays <- aggregate(weekdaysdata$steps, by=list(interval=weekdaysdata$interval),fun=mean)
weekendsdata <- finaldata[!finaldata$isweekday,]
stepsperinterval-weekends <- aggregate(weekendsdata$steps, by=list(interval=weekendsdata$interval), fun=mean)
colnames(stepsperintervalweekdays) <- c("interval", "average_steps")
colnames(stepsperintervalweekends) <- c("interval", "average_steps")
stepsperintervalweekdays$day <- "Weekday"
stepsperintervalweekends$day <- "Weekend"
weekdata <- rbind(stepsperintervalweekends, stepsperintervalweekdays)
weekdata$day <- as.factor(weekdata$day)
xyplot(average_steps ~  interval | day, data = weekdata, layout = c(1,2), type ="l", ylab="Number of Steps")
```

